Modelling the Co-evolution of Trade and Culture in Past Societies

### 2015-07-01 article.tex
fix algo selection process
finalise the algorithm and remove a figure to gain space

\begin{figure}[htp]
	\begin{center}
		\includegraphics[width=7cm]{img/fitness.pdf}
	\end{center}
	\caption{The payoff depending on the quantity owned of a given good and the effective needs $n(g)$ for this good.}
	\label{fig:fit}
\end{figure}
Figure~\ref{fig:fit} depicts the score of an agent, for different need values of one good, with regards to the quantity of the good possessed by the agent. We can see that even if the need for a good is small (for instance when $n(g) = 0.01$) an agent can have a high score as soon as it manages to get a quantity close to the need. This ensures that an agent needs to have for each of the good a quantity equal to the need and that no agent could reach a better score just by getting the right quantity for a good with a high need.

@@

\todo{Arreglar : how to say ``we choose a random number and if it's less that (or more than) the relative score we continue}
\begin{algorithm}
\caption{Selection Process}
\label{algo:selectionCulture}
	\begin{algorithmic}[1]
	\scriptsize
	\State	$toGet = 0.2 \times \#Pop$
	\For{$g \in Good$}
		\State	$toChange = \{\}$
                \While{$\#toChange < toGet$}
			\State $ j = rand(Pop,g) $ 
			\If{$P(X<ComputeScore(j))$}
				\State $toChange = \{toChange,j\}$
			\EndIf
		\EndWhile

                \While{$\#toChange > 0 $}
			\State $ j = rand(toChange) $ 
			\State $ i = rand(Pop,g) $ 
			\If{$P(X>ComputeScore(j)>ComputeScore(i))$}
				\State copyPrice(i,j)	
				\State $toChange = toChange - i$
			\EndIf

>>>>

%\begin{figure}[htp]
%	\begin{center}
%		\includegraphics[width=7cm]{img/fitness.pdf}
%	\end{center}
%	\caption{The payoff depending on the quantity owned of a given good and the effective needs $n(g)$ for this good.}
%	\label{fig:fit}
%\end{figure}
%Figure~\ref{fig:fit} depicts the score of an agent, for different need values of one good, with regards to the quantity of the good possessed by the agent. We can see that even if the need for a good is small (for instance when $n(g) = 0.01$) an agent can have a high score as soon as it manages to get a quantity close to the need. This ensures that an agent needs to have for each of the good a quantity equal to the need and that no agent could reach a better score just by getting the right quantity for a good with a high need.

@@

\begin{algorithm}
\caption{Selection Process}
\label{algo:selectionCulture}
	\begin{algorithmic}[1]
	\scriptsize
	\State	$ToGet = 0.2 \times \#Pop$
	\For{$g \in Good$}
		\State	$ToReplace = \{\}$
                \While{$\#ToReplace < ToGet$} 
			\State $ j = SelectRand(Pop,g) $ \Comment{Select randomly an agent $j$ among the agents producing $g$}
			\State $X \sim U([0,1])$ \Comment{Draw a random number from the uniform distribution between 0 and 1}
			\If{$X>ComputeScore(j)$} \Comment{Select preferably the agents with the lowest scores}
				\State $ToReplace = \{ToReplace,j\}$
			\EndIf
		\EndWhile

                \While{$\#ToReplace > 0 $}
			\State $ j = SelectRand(ToReplace) $ 
			\State $ i = SelectRand(Pop,g) $  \Comment{Select randomly an agent $i$ among the agents producing $g$}
			\State $X \sim U([0,1])$ 
			\If{$ (X<ComputeScore(i))$} \Comment{Select preferably an agent $i$ with a high score}
				\If {$ (ComputeScore(i)>ComputeScore(j))$} \Comment{Verify that agent $i$ has a higher score than agent $j$}
					\State $CopyPrice(i,j)$
					\State $ToReplace = ToReplace - i$
				\EndIf
			\EndIf
